%______________________________________________________________________________________________________________________
% @brief    LaTeX2e Resume for Alhaad Gokhale
\documentclass[margin,line]{resume}


%______________________________________________________________________________________________________________________
\begin{document}
\name{\Large Alhaad Gokhale}
\begin{resume}

    %__________________________________________________________________________________________________________________
    % Contact Information
    \section{\mysidestyle Contact\\Information}

    GitHub: alhaad                            \hfill phone: +1 650 889 6793          \vspace{0mm}\\\vspace{0mm}%
    LinkedIn: alhaadgokhale                          \hfill e-mail: alhaadgokhale[AT]gmail.com          \vspace{0mm}\\\vspace{0mm}%
    \hfill e-mail: alhaad[AT]google.com  \vspace{0mm}\\\vspace{-4.5mm}%


    %__________________________________________________________________________________________________________________
    % Areas of Interests
    \section{\mysidestyle Areas Of\\Interests}

    Operating systems, Distributed systems, Theoretical computer science.

    %__________________________________________________________________________________________________________________
    % Work Experience
    \section{\mysidestyle Work\\Experience}

    \textbf{Google Inc}, Mountain View, California \hfill \textbf{Senior Software Engineer} \vspace{2mm}\\\vspace{1mm}%
    \textsl{Fuchsia} \hfill \textbf{Jan 2015 -- present}\\
    Working on Fuchsia, a new operating system by Google.
    https://fuchsia.googlesource.com/

    \textbf{Google Inc}, Mountain View, California \hfill \textbf{Software Engineer} \vspace{2mm}\\\vspace{1mm}%
    \textsl{Search Infrastructure} \hfill \textbf{Oct 2013 -- Dec 2014}\vspace{1.5mm}\\\vspace{0mm}%
   Worked with Search Infrastructure Serving team which is responsible for handling all search queries that come to Google. 

    \textbf{Google Inc}, Mountain View, California \hfill \textbf{Intern} \vspace{2mm}\\\vspace{1mm}%
    \textsl{Crawler} \hfill \textbf{May 2012 -- July 2012}\\
    Worked with Crawl-Scheduler team which is responsible for determining the rate at which a website is recrawled by Google.

    \textbf{Nucleodyne Systems Inc}, Cupertino, California \hfill \textbf{Intern} \vspace{2mm}\\\vspace{1mm}%
    \hfill \textbf{May 2011 -- July 2011}\\
    Ported a power-aware implementation of the USB protocol stack on a bare-metal Power-PC based platform.

   \textbf{National Center For Supercomputing Applications}, UIUC \hfill \textbf{Intern} \vspace{2mm}\\\vspace{1mm}%
    \hfill \textbf{May 2010 -- July 2010}\\
    Developed a model to quantify symmetry and randomness in a noisy image pattern.

    %__________________________________________________________________________________________________________________
    % Education
    \section{\mysidestyle Education}

    \textbf{Indian Institute of Technology}, Kharagpur \vspace{2mm}\\\vspace{1mm}%
    \textsl{B.Tech.(Hons) + M.Tech.}, Computer Science and Engineering \hfill \textbf{ 2008 -- 2013}\vspace{-3mm}\\\vspace{-1mm}%

    %__________________________________________________________________________________________________________________
    % Honours and Awards
    \section{\mysidestyle Honours and\\Awards} 

    \begin{list2}
        \item National Talent Search (NTS) Scholar
        \item Kishore Vaigyanik Protsahan Yojana (KVPY) Scholar
        \item Apeejay Talent Search (ATS) Scholar
        \item Secured an All-India Rank of 612 in the IIT Joint Entrance Examination, 2008
        \item Finalist for National Physics and Mathematics Olympiads
    \end{list2}\vspace{-1.5mm}


    %__________________________________________________________________________________________________________________
    % Publications
    \section{\mysidestyle Publications}

    Datta, Kamalika and Gokhale, Alhaad and Sengupta, Indranil and Rahaman, Hafizur, 
    ``An esop-based reversible circuit synthesis flow using simulated annealing'',
    \textsl{Applied Computation and Security Systems}, pp. 131-144, 2015, Springer India.

\vspace{-2mm}
    Gokhale, Alhaad and Bajcsy, Peter,
    ``Automated classification of quilt photographs into crazy and non-crazy'',
    In \textsl{IS\&T/SPIE Electronic Imaging}, 2011.
    
    %__________________________________________________________________________________________________________________
    % Patents
    \section{\mysidestyle Patents}

    Gokhale, Alhaad and Brown, Jeff and Meschkat, Steffen and Giesing, Kris, 
    ``System And Method For Automatically Synchronizing Responses To Conditions On Devices'',
    US Patent Application 15/808,153, filed November 2017. Patent pending.

    %__________________________________________________________________________________________________________________
    % Computer Skills
    \section{\mysidestyle Programming} 

    C, C++, Python, Java, Dart.


%______________________________________________________________________________________________________________________
\end{resume}
\end{document}


%______________________________________________________________________________________________________________________
% EOF
